Capstone Movielens Report

### 2025-12-12 reports/capstone-movielens.site/05.appendix.Rmd
Fix for functions: UMGY_SmoothedDay_effect.predict.

Predicts *user rating* values on the *Test dataset* passed in the [test_set](#func.UMGY_SmoothedDay_effect.predict.args.test_set) argument based on the data of the trained *UMGY Effect (UMGYDE) Model* passed in the [day_smoothed_effect](#func.UMGY_SmoothedDay_effect.predict.args.day_smoothed_effect) argument.

@@

:::
::: { #func.UMGY_SmoothedDay_effect.predict.args.day_smoothed_effect .sidebar }
  - **day_smoothed_effect:** Data frame representing the *UMGYDE Model*.

@@

Dataframe containing *predicted user rating values* based on the *UMGYDE Model*
:::

>>>>

Predicts *user rating* values on the *test dataset* passed in the [test_set](#func.UMGY_SmoothedDay_effect.predict.args.test_set) argument based on the data of the trained *UMGY Effect (UMGYDE) Model* passed in the [day_smoothed_effect](#func.UMGY_SmoothedDay_effect.predict.args.day_smoothed_effect) argument.

@@

:::
::: { #func.UMGY_SmoothedDay_effect.predict.args.day_smoothed_effect .sidebar }
  - **day_smoothed_effect:** Dataframe object representing the *UMGYDE Model*.

@@

Dataframe object containing *predicted user rating* values based on the *UMGYDE Model*
:::
